\Huge \bf \sc Calibration of an inertial measurement unit

### 2013-07-30 latex/paper_sensores/paper.tex
ahora si listo

In equation \refp{eq:calib_temp}, $N = 22740$\footnote{This number is not needed to be this big, yet all the data of the cooling process was used (see figure \ref{fig:bajada}).} is the number of samples took, $\mathbf{T}_{s0}^p$, $\mathbf{K_{s0}}$ are the matrix obtained in the static parameter calibration (ambiance temperature) and $\mathbf{b}_s(T)$ is the vector defined in \refp{eq:temp}. This last vector includes the variable to be estimated.\\

>>>>

In equation \refp{eq:calib_temp}, $\mathbf{T}_{s0}^p$, $\mathbf{K_{s0}}$ are the matrix obtained in the static parameter calibration (ambiance temperature), $\mathbf{b}_s(T)$ is the vector defined in \refp{eq:temp} and $N = 22740$ is the number of measured samples. There is no need of so many samples, yet all the data of the cooling process was used (see figure \ref{fig:bajada}). Vector $\mathbf{b}_s(T)$ includes the variable to be estimated.\\
